%==============================================================================
% DEVELOPER RESUME - Rishita Tiwari
% Compile with: pdflatex developer_resume.tex
%==============================================================================

\documentclass[11pt, a4paper]{article}

%------------------------------------------------------------------------------
% PACKAGES
%------------------------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[margin=1.8cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{parskip}

%------------------------------------------------------------------------------
% COLORS
%------------------------------------------------------------------------------
\definecolor{accent}{HTML}{B8860B}   % Gold accent (Matching PRAVAH theme)
\definecolor{darkgray}{HTML}{111827}
\definecolor{medgray}{HTML}{374151}
\definecolor{lightgray}{HTML}{6B7280}
\definecolor{rulecol}{HTML}{F3F4F6}

%------------------------------------------------------------------------------
% HYPERLINK STYLE
%------------------------------------------------------------------------------
\hypersetup{
    colorlinks=true,
    urlcolor=accent,
    linkcolor=accent,
    pdftitle={Rishita Tiwari - Resume},
}

%------------------------------------------------------------------------------
% SECTION FORMATTING
%------------------------------------------------------------------------------
\titleformat{\section}
    {\large\bfseries\color{darkgray}}
    {}{0em}{}
    [\vspace{-4pt}\textcolor{rulecol}{\hrule height 1.5pt}\vspace{4pt}]

\titlespacing{\section}{0pt}{10pt}{4pt}

%------------------------------------------------------------------------------
% CUSTOM COMMANDS
%------------------------------------------------------------------------------

\newcommand{\resumename}[1]{%
    {\Huge\bfseries\color{darkgray} #1}%
}

\newcommand{\contactrow}[1]{%
    \vspace{4pt}
    {\small\color{medgray} #1}%
}

\newcommand{\entry}[4]{%
    \noindent
    \begin{tabularx}{\linewidth}{@{}X r@{}}
        {\bfseries\color{darkgray} #1} \, {\color{accent}$|$} \, {\color{medgray}\itshape #2} &
        {\small\color{lightgray} #4 \quad #3}
    \end{tabularx}%
    \vspace{1pt}%
}

\newenvironment{bullets}{%
    \begin{itemize}[leftmargin=1.2em, itemsep=1pt, topsep=2pt, parsep=0pt]
    \small\color{darkgray}
}{%
    \end{itemize}
}

\newcommand{\skillcat}[2]{%
    \noindent{\bfseries\color{darkgray} #1: } {\small\color{medgray} #2}\\[3pt]%
}

%------------------------------------------------------------------------------
% DOCUMENT
%------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%==============================================================================
% HEADER
%==============================================================================
\begin{center}
    \resumename{Rishita Tiwari}\\[6pt]
    \contactrow{%
        \faMapMarker* \, Navi Mumbai, India \quad
        \faPhone* \, +91 [Your Phone] \quad
        \faEnvelope[regular] \, \href{mailto:tiwaririshita@example.com}{tiwaririshita@example.com} \quad
        \faGithub \, \href{https://github.com/Riri2018}{github.com/Riri2018} \quad
        \faLinkedin \, \href{https://linkedin.com/in/rishita-tiwari}{linkedin.com/in/rishita-tiwari}
    }
\end{center}

\vspace{2pt}

%==============================================================================
% SUMMARY
%==============================================================================
\section{Summary}
Computer Engineering student with a strong focus on AI/ML and Full-stack Web Development. Passionate about building intelligent systems that solve real-world problems. Experienced in Python, JavaScript, and modern frameworks like FastAPI and Next.js. Recently developed a high-precision house price prediction system for Navi Mumbai using advanced Gradient Boosting algorithms.

%==============================================================================
% EDUCATION
%==============================================================================
\section{Education}

\entry{B.E. in Computer Engineering}{Lokmanya Tilak College of Engineering}{2023 -- 2027 (Expected)}{Navi Mumbai}
\begin{bullets}
    \item Currently in 2nd Year. 
    \item Relevant Coursework: Data Structures \& Algorithms, Object-Oriented Programming, Database Management Systems, Discrete Mathematics.
\end{bullets}

%==============================================================================
% TECHNICAL SKILLS
%==============================================================================
\section{Technical Skills}

\skillcat{Languages}{Python, JavaScript, TypeScript, HTML/CSS, SQL, Java}
\skillcat{AI \& Data Science}{Scikit-learn, Pandas, NumPy, Gradient Boosting, Data Cleaning, Model Validation}
\skillcat{Web Development}{Next.js, FastAPI, Node.js, Tailwind CSS, React.js}
\skillcat{Databases}{PostgreSQL, MongoDB, SQL Server}
\skillcat{Tools}{Git/GitHub, Docker, Render, Vercel, VS Code, LaTeX}

%==============================================================================
% PROJECTS
%==============================================================================
\section{Projects}

%--- Project 1 ---
\entry{PRAVAH - Navi Mumbai House Price Prediction AI}{\href{https://github.com/Riri2018/PRAVAH-Project}{github.com/Riri2018/PRAVAH-Project}}{2026}{}
\begin{bullets}
    \item Developed a full-stack ML application predicting property prices in Navi Mumbai with \textbf{94\% accuracy}.
    \item Engineered a \textbf{GradientBoostingRegressor} pipeline handling 2,500+ listings and 15+ location clusters.
    \item Built a high-performance backend using \textbf{FastAPI} and a premium "Midnight Gold" frontend with \textbf{Next.js 14}.
    \item Implemented cinematic reveal animations and glassmorphism for enhanced user experience.
\end{bullets}
\vspace{6pt}

%--- Project 2 ---
\entry{Resource Allocation System}{Strategy Management Tool}{2025}{}
\begin{bullets}
    \item Built an allocation system for team-based competition strategy management.
    \item Implemented role-based access for moderators and participants with real-time data persistence.
    \item Generated automated performance reports and presentation-style slides for each team.
\end{bullets}
\vspace{6pt}

%--- Project 3 ---
\entry{Developer Resume Template}{LaTeX, Custom Styling}{2025}{}
\begin{bullets}
    \item Designed a clean, professional LaTeX template for developers to maintain version-controlled resumes.
\end{bullets}

%==============================================================================
% ACHIEVEMENTS & CERTIFICATIONS
%==============================================================================
\section{Achievements \& Certifications}

\begin{bullets}
    \item \textbf{Academic Excellence}: Consistently maintained a strong SGPA in the first three semesters of Engineering.
    \item \textbf{Open Source}: Actively contributing to personal and academic projects on GitHub.
    \item \textbf{Technical Certification}: Completed courses in Professional Web Development and Python for Data Science.
\end{bullets}

\end{document}
